Final analysis for paper

### 2020-08-10 inst/rmd/aug2020/aug2020.Rmd
implemented new modeling

# SIMULATIONS
sim_data <- simulations
sim_data$idx <- sim_data$oracle_number
fe <- getfe(final_model)
predictions <- exp(predict(final_model_lm, sim_data, interval = 'confidence'))-1
predictions <- data.frame(predictions)
# Add the fixed effects
fixed_effects <- left_join(sim_data,
                           data.frame(fe) %>% dplyr::select(idx, effect) %>%
                             mutate(idx = as.character(idx))) %>%
  .$effect
fixed_effects <- as.numeric(fixed_effects)

predictions$fit <- predictions$fit + fixed_effects
predictions$lwr <- predictions$lwr + fixed_effects
predictions$upr <- predictions$upr + fixed_effects

# combine other info
predictions <- predictions %>% bind_cols(sim_data %>% dplyr::select(date, absent, strategy, permanent_or_temporary)) %>%
  mutate(absent = as.numeric(absent)) %>%
  filter(!is.na(fit))

>>>>

# TO DO: MAKE PREDICTIONS BASED ON INDIVIDUAL MODEL TYPES

# SIMULATIONS
sim_data <- simulations  %>% filter(on_site)
sim_data$idx <- sim_data$oracle_number
sim_data$fit <- NA
# Multi model predictions
for(i in 1:length(worker_groups)){
  this_worker_group <- worker_groups[i]
  indices <- which(sim_data$group == this_worker_group)
  this_data <- sim_data[indices,]
  this_model_fix <- model_list_fix[[this_worker_group]]
  these_predictions <- exp(predict(this_model_fix, this_data))-1
  sim_data$fit[indices] <- these_predictions
}
predictions <- sim_data %>% filter(!is.na(fit))

# # One model predictions
# fe <- getfe(final_model)
# predictions <- exp(predict(final_model_lm, sim_data, interval = 'confidence'))-1
# predictions <- data.frame(predictions)
# # Add the fixed effects
# fixed_effects <- left_join(sim_data,
#                            data.frame(fe) %>% dplyr::select(idx, effect) %>%
#                              mutate(idx = as.character(idx))) %>%
#   .$effect
# fixed_effects <- as.numeric(fixed_effects)
# 
# predictions$fit <- predictions$fit + fixed_effects
# predictions$lwr <- predictions$lwr + fixed_effects
# predictions$upr <- predictions$upr + fixed_effects
# 
# # combine other info
# predictions <- predictions %>% bind_cols(sim_data %>% dplyr::select(date, absent, strategy, permanent_or_temporary)) %>%
#   mutate(absent = as.numeric(absent)) %>%
#   filter(!is.na(fit))
